---
title: "Lab 8"
author: "Katheryn Moya"
date: "11/16/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(modelsummary)
library(corrplot)
library(broom)
library(here)
```

## read in slo_homes.csv

```{r}
homes <- read_csv(here("data","slo_homes.csv"))
```

## Create a subset with 4 cities
Task: create a subset (called homes_subset) that only contains observations where the city is:

- "San Luis Obispo"
- "Atascadero"
- "Arroyo Grande"
- "Santa Maria-Orcutt"

```{r}
homes_subset <- homes %>% 
  filter(City %in% c("San Luis Obispo", "Atascadero", "Arroyo Grande", "Santa Maria-Orcutt"))
```

### A little exploration

Task: Using the subset you just made, create a summary table that has the mean and standard deviation of home prices grouped by city and sale status

```{r, include = FALSE}
homes_subset %>% 
  group_by(City, Status) %>% # if you have multiple variables, will nest them into groups
  summarize(mean_price = mean(Price),
            sd_price = sd(Price),
            mean_sqft = mean(SqFt))
  
# if you put eval = FALSE, code chunk won't even run
```

Task: explore the relationship between square footaage and home price (from homes_subset) in a scatterplot.

```{r}
ggplot(data = homes_subset, aes( x = SqFt, y = Price)) +
  geom_point() +
  geom_smooth(method = "lm")
```

Based on this trend, I may expect a house this size to be XXX, but instead it is XXX


### Try a few linear models

Use multiple linear regression to investigate relationships between several predictor variables and home price


Task: create two different permutations of this model:
(1) price ~ city, bedrooms, bathrooms, sqft, status (lm1)
(2) price ~ city, sqft, status (lm2)
(3) try another one (lm3)

```{r}
lm1 <- lm( Price ~ City + Bedrooms + Bathrooms + SqFt + Status, data = homes_subset)

lm1

lm2 <- lm( Price ~ City + SqFt + Status, data = homes_subset)

lm2

lm3 <- lm( Price ~ City + SqFt, data = homes_subset)

lm3

# if i wanted SLO to be the reference level:
# use fct_relevel to specify a new reference level

new_homes_subset <- homes_subset %>% 
  mutate(City = fct_relevel(City, "San Luis Obispo"))

lm_slo <- lm(Price ~ City + SqFt + Status, data = new_homes_subset)

lm_slo

summary(lm_slo)

```
54% variance in home price is captured/explained by this model 


### Explore correlations between quanititative variables 

Task: make a subset called homes_quant (starting from homes_subset) that only contains the variables from Price through SqFt

```{r}
homes_quant <- homes_subset %>% 
  select(Price:SqFt)

#find correlations

homes_cor <- cor(homes_quant)
```


### Compare AIC values

```{r}
AIC(lm1)
AIC(lm2)
```
lower AIC indicates better balance

### use modelsummary() to return multiple model outputs

```{r}
modelsummary(list(lm1, lm2, lm3))
```

### check out diagnostic plots for lm1

```{r}
plot(lm1)
```
### use broom::augment() to return the predictions for existing observations

```{r}
home_predictions <- augment(lm1)

# make a histogram of the residuals of this model

ggplot(data = home_predictions, aes(x = .resid)) +
  geom_histogram()
```

